Analyzing the Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-03 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

two <- z.test(x=game_log_2020_home$PTS, y=game_log_2017_2019_home$PTS, sigma.x = 
                sd(game_log_2020_home$PTS), sigma.y = sd(game_log_2017_2019_home$PTS))
rowtwo <- c(as.numeric(two$estimate[1]), as.numeric(two$estimate[2]), 
            two$conf.int, two$statistic, two$p.value)

three <- z.test(x=game_log_2020_away$PTS, y=game_log_2017_2019_away$PTS, sigma.x = 
                  sd(game_log_2020_away$PTS), sigma.y = sd(game_log_2017_2019_away$PTS))
rowthree <- c(as.numeric(three$estimate[1]), as.numeric(three$estimate[2]), 
              three$conf.int, three$statistic, three$p.value)

>>>>

two <- z.test(x=game_log_2020_home$PTS, y=game_log_2017_2019_home$PTS, sigma.x = 
                sd(game_log_2020_home$PTS), sigma.y = sd(game_log_2017_2019_home$PTS))
rowtwo <- c(as.numeric(two$estimate[1])/100, as.numeric(two$estimate[2])/100, 
            two$conf.int, two$statistic, two$p.value)

three <- z.test(x=game_log_2020_away$PTS, y=game_log_2017_2019_away$PTS, sigma.x = 
                  sd(game_log_2020_away$PTS), sigma.y = sd(game_log_2017_2019_away$PTS))
rowthree <- c(as.numeric(three$estimate[1])/100, as.numeric(three$estimate[2])/100, 
              three$conf.int, three$statistic, three$p.value)
